---
title: "Group Project Data Managing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


[How to get API Key!?!?!?!?!?!](https://developer.riotgames.com/)
1. Click the link above
2. Sign in (or Sign up). If you have played League of Legends, the ID and password for League of Legends is the one you need here.
3. On the left below, there's an API key.

```{r}
APIkey = "RGAPI-5f9ec25e-6ac2-4d82-9e56-3a5612c9b512" 
# Everyone will have different API key

```

Prompt user to input game ID (A name that appears in the game) to get the unique serial number representing that ID.
```{r get_id}
# install.packages("jsonlite") : install "jsonlite" package to use API
library(jsonlite) # load jsonlite library


get_id = function() {
  name = readline("Type in your Game ID : ") # Prompt user to input game id
  
  Summonerurl <- paste("https://na.api.pvp.net/api/lol/na/v1.4/summoner/by-name/",name,"/?api_key=",APIkey, sep = "")
  # Get the url of requested api data
  
  SummonerID <- fromJSON(Summonerurl) # Get the api data into "SummonerID" variable
  
  id = SummonerID[[1]]$id
   # From Riot's API and a given game id, get the unique serial numbers for that id and assign this numeric values into "id" variable
  return(id)
}
```

Get information about champion.

We need to know each champion's unique id. 

First, we are going to make a dataset containing all champion's id and add another column that has champion's name corresponding to their unique id.
```{r champ_info}
champ_info = function() {
  championurl <- paste("https://na1.api.riotgames.com/lol/static-data/v3/champions?locale=en_US&dataById=false&api_key=",APIkey, sep="")
  champions <- fromJSON(championurl)
  # Get all champions data including id and name from Riot's API
    
  x = matrix(,length(champions[[1]]),2)
  # Create a empty matrix with 2 columns and 137 rows so that it can contain id and name of 137 champions in each row
  
  for(i in 1:137) {
    x[i,] = c(champions[[1]][[i]]$id, champions[[1]][[i]]$name) 
    # In each row, add champion id on first column and name no second column
  }
  return(x)
  # If this function is called, it will return the matrix containing id and names of all champions
}
```

By using the result dataset (matrix) from above, we will ask user to input which champion they pick and will make a function to return the id of that chosen champion
```{r get_champ_id}
get_champ_id = function() { # A function to get champion unique id number if user input champion's name (case insensitive)


  championurl <- paste("https://na1.api.riotgames.com/lol/static-data/v3/champions?locale=en_US&dataById=false&api_key=",APIkey, sep="")
  champions <- fromJSON(championurl)
  # Get all champions data including id and name from Riot's API
  
  champ_name = readline("What champion did you pick? : ")
  # Prompt user to input champion name they picked
  
  champ_table = champ_info()
  # Load champion data by calling champ_info function.
  # Champion data table will contain ID in first column and Name in second column
  
  for(i in 1:137) { # For loop to check all champion data table
    
    if(toupper(champ_name) == toupper(champ_table[i,2])) { 
      # If chosen champion name equals to the value in champion data table's second column of a specific row,
      return(champ_table[i,1]) # Then, return the value in first column in the same row
    }
  }
}
```

If user input game ID, and champion picked.
This will provide the statistics of the player's performances with that chosen champion.
```{r get_personal_champ_stat}
get_personal_champ_stat = function() {
  
  summonerid = get_id() # Get user to input their game id and store the function return value (summonerID) in "summonerid"" variable
  champ_id = as.numeric(get_champ_id()) # Get user to input their chosen champion's name and store the function return value (championID) in "champ_id"" variable as numeric value
  
  staturl <- paste("https://na.api.riotgames.com/api/lol/NA/v1.3/stats/by-summoner/",summonerid,"/ranked?season=SEASON2017&api_key=", APIkey, sep = "")
  stat <- fromJSON(staturl)
  # With the given summonerid, get the player's game statistics 
  # This dataset will include various data for each champion they have played in the chosen season (2017)
  
  
  personal_champ_stat_data = matrix(,1,length(stat[[3]][[2]]))
  # Create a empty 1 row matrix that will contain all data with the chosen champion
  
  if(!(champ_id %in% stat[[3]][[1]])) { # If chosen champion is not in the dataset,
    cat("You haven't played this champion.") # Then, it means, the user haven't played that champion before
  }
  
  
  for(i in 1:length(stat[[3]][[1]])) { 
    
    if(champ_id == stat[[3]][[1]][i]) {
      personal_champ_stat_data = stat[[3]][i,] 
    }
  
  }
  
  return(personal_champ_stat_data)
    
}


```

From the statistic data of a chosen champion, we can get the total game played and won with that specific champion. Then, we can get the personal win rate of tha champion.
```{r get_personal_champ_win_rate}
get_personal_champ_win_rate = function() {
  stat <- get_personal_champ_stat()
  total_played = stat[[2]]$totalSessionsPlayed
  total_win = stat[[2]]$totalSessionsWon
  
  win_rate = total_win / total_played * 100
  
  return(win_rate)
}
```







We also need overall average win rate in each tier for all champions.
Let's use web scrapping this time
```{r web_bronze_stat}
# install.packages("rvest")
library(rvest)

get_web_stat_bronze = function() {
  
  stat_bronze = read_html("http://www.leagueofgraphs.com/champions/stats/bronze")
  
  stat_bronze %>%
    html_nodes(xpath = '//*[@id="mainContent"]/div/div/div/table') %>%
    html_table(fill = TRUE) -> champ_stat_bronze
  
  champ_stat_bronze[[1]]$Name %>% 
    grep("          \r\n", x = ., value = T) %>%
    gsub("\r\n.*", "", x = .) %>%
    sub(" .*", "", x = .) -> web_champ_name_bronze
  
  
  champ_stat_bronze[[1]]$WinRate %>%
    grep("          \r\n", x = ., value = T) %>%
    gsub("\r\n.*", "", x = .) -> web_champ_win_rate_bronze
  
  web_bronze_stat = matrix(c((web_champ_name_bronze), (web_champ_win_rate_bronze)), ncol = 2)
  return(web_bronze_stat)

}
```




